%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Research \& Professional Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Security Incident Response Team | Synology Inc.} % Organization
{Product Developer} % Job title
{New Taipei City, Taiwan} % Location
{Oct. 2019 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Discovered and reported an ARM32-specific denial-of-service vulnerability in ClamAV, contributing to upstream security remediation.
\item Migrated DSM Security Advisor, Control Panel, and AntiVirus modules from Ext.js to Vue 3, leveraging LLM-assisted code transformation to accelerate large-scale legacy UI modernization.
\item Designed a hardware-aware producer–consumer scanning pipeline for AntiVirus Essential (ClamAV) with adaptive multi-threading and ring-queue scheduling, reducing scan time by 50\% while maintaining stable CPU and memory utilization.
\item Integrated Hardware Security Module (HSM) into firmware signing workflow using RSA signatures to protect Synology camera firmware integrity.
\item Architected a company-wide SBOM platform integrating build pipeline, container registries (Harbor/GitLab), AWS, and Kubernetes environments with Trivy and ClamAV scanning to detect vulnerable components.
\item Developed an internal Incident Response platform (Python/Django) aggregating MITRE CVE, CISA KEV, EPSS, RSS, Crawler, SentinelOne telemetry, dark web intelligence, and bounty program workflows for vulnerability prioritization and tracking.
\item Built automated firewall log correlation and analysis system to identify suspicious network behavior and support proactive threat mitigation.
\end{cvitems}
}

%------------------------------------------------

\cventry
{Department of Information Management | NSYSU} % Organization
{Graduate Researcher in Intelligence Defensive System Laboratory} % Job title
{Kaohsiung, Taiwan} % Location
{Sep. 2015 - Jul. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Utilized Machine Learning to evaluate security incident logs from Checkpoint and ArcSight about Advanced Persistent Threats (APT).}
\item {Migrated Hadoop and Spark cluster from Xen to Docker environment and promoted an over 50\% performance increase.}
\item {Systemized a high throughput pipeline with Fluentd, Kafka, Spark, MongoDB clusters on Docker to analyze 1TB real-time log data.}
\item {Created an automatic deployment of Hadoop and Spark standalone cluster script on DockerHub and brought out 300+ downloads.}
\item {Lectured the deployment and usages of Hadoop, Spark and Docker for over 40 graduate students in a financial trading program.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Taiwan Ministry of Education} % Organization
{Trainee of Advanced Information Security Summer School (AIS3)} % Job title
{Kaohsiung, Taiwan} % Location
{Aug. 2016 - Aug. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Enhanced practical skills through the actual combats and the sharing of related experience in the information security field.}
\end{cvitems}
}

%------------------------------------------------

% \cventry
% {Department of Information Management | NSYSU} % Organization
% {Teaching Assistant of Network Security / Cloud Computing / Operating System} % Job title
% {Kaohsiung, Taiwan} % Location
% {Sep. 2015 - Jan. 2017} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Deployed and maintained a CTF platform by using Docker and organized a CTF competition for 30+ graduate students.}
% \item {Designed, built and collected over 20 CTF challenges in Web, MISC, Cryptography and Steganography categories for the CTF platform.}
% \item {Graded assignments and conducted consultations for 30+ graduate students about final project presentations for Cloud Computing.}
% \item {Graded exams and conducted consultations for 50+ undergraduate students about final project presentations for Operating System.}
% \item {Designed and presented 16 personal seminars and 2 exam preparation sessions on special topics for Operating System.}
% \end{cvitems}
% }

%------------------------------------------------
  
\end{cventries}
